The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-03 paper/Analisis.tex
Paragraph about mu anular dependency

As a primer approach we study the angular dependency in the same manner as
we do in section \ref{sec:results}, but with the set up of the off-center models
where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis,  the observer is 
located at . In Fig. \ref{fig:OCflux} the angular 
dependency for two different off-center distribution are shown. the bold line  
represents an off center sphere located at $0.25 R$ in the homogeneous sphere, while 
the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
show exactly the same trend. We find a high dependency in the viewing angle,
in particular observers at .

@@

There are two new morphological features that off-center emission in 
rotating galaxies produces. First in some of our models with specific 
values of velocity and optical depth an asymmetry in the peak heights 
is presented, those off-center spheres \textit{(put image reference)} 
located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
present a higher peak in the redshifted part, while those spheres located
at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.

>>>>

As a primer approach we study the angular dependency in the same manner as
we do in section \ref{sec:results}, but with the set up of the off-center models
where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
located at $\mathrm{\theta = \pi/2}$. In Fig. \ref{fig:OCflux} the angular 
dependency for two different off-center distribution are shown. The bold line  
represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
show exactly the same trend. We find a high dependency in the viewing angle
in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
galaxies are oriented in random directions which implies that off-center emission
is not going to be observed in all the observed galaxies.

@@

There are two new morphological features that off-center emission in 
rotating galaxies produces. First in some of our models with specific 
values of velocity and optical depth an asymmetry in the peak heights 
is presented, those off-center spheres \textit{(put image reference)} 
located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
present a higher peak in the red-shifted part, while those spheres located
at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ 
where one peak is $20\%$ higher than the other.
